The \dealii{} Library, Version 9.3

### 2021-06-21 9.3/paper.tex
Remove a TODO.
Fix typo

  \item A long standing orientation issue for the vector valued finite
  element \texttt{FE\_RaviartThomas<3>} was resolved. This issue
  prevented the user from using this class on meshes with cells that
  do not have standard orientation, i.e., cells that have faces that
  are reflected and/or rotated relative to their neighbors. In all eight
  possible neighboring configurations, we can now guarantee that the
  necessary $H(\mathrm{div})$-conformity condition is met for all
  polynomaial orders. This is verified through a new conformity test
  on non-standard meshes.
\end{itemize}
%
The changelog lists more than 200 other features and bugfixes.

@@

\todo[inline]{Everyone update. Add support for any additional authors.}

>>>>

  \item A long standing orientation issue for the vector valued finite
  element \texttt{FE\_RaviartThomas<3>} was resolved. This issue
  prevented the user from using this class on meshes with cells that
  do not have standard orientation, i.e., cells that have faces that
  are reflected and/or rotated relative to their neighbors. In all eight
  possible neighboring configurations, we can now guarantee that the
  necessary $H(\mathrm{div})$-conformity condition is met for all
  polynomial orders. This is verified through a new conformity test
  on non-standard meshes.
\end{itemize}
%
The changelog lists more than 200 other features and bugfixes.

@@
